---
title: "Data Summary"
author: "Nayaeun Kwon"
date: '2022-10-21'
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

Importing datasets and necessary packages
```{r inlcue=FALSE}
#Importing Datasets
movie <- read.csv("movie_reduced.csv")
str(movie)
summary(movie)

newmovie <- na.omit(movie)
xkablesummary(newmovie)
```

```{r include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ezids)
library(scales)


knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scipen=999)
```

--------------------------------------------------------------------------
# 1. Independent Variables EDA: Overview of Data
### 1.1 Overview for Domestic Lifetime Gross 

```{r }
summary(newmovie)
sd(newmovie$dlg)
```

Refined dataset yields following observations for the domestic lifetime gross of ranked movies: the minimum price is $`r min(movie$dlg)` and the maximum price is $`r max(movie$dlg)`; the mean of gross is $`r mean(movie$dlg)` (indicating mean is higher than median ($`r median(movie$dlg)`) which means the shape of distribution is right-skewed); the standard deviation of gross is $`r sd(movie$dlg)`.

x="Gross of Movie ($)",   xlim (NA, 100000000)  + 
```{r Plots for dlg}
# Histogram
ggplot(newmovie, aes(x=dlg)) + 
  geom_histogram(col='dark blue', fill='light blue', bins = 30) + 
  labs(title = "Histogram of Domestic Lifetime Gross",  y="Frequency") + 
  theme(plot.title = element_text(hjust = 0.5))+
  scale_x_continuous("Lifetime Gross of Movie($)", limits= c(NA, 35000000), labels = label_number_si())

#Box plot
ggplot(newmovie, aes(y=dlg)) +
  geom_boxplot(na.rm = T, colour="sky blue", outlier.colour="dark blue", outlier.shape=8, outlier.size=4) +
  coord_cartesian(ylim = c(0,100000000)) +
  labs(title = "Boxplot of Domestic Lifetime Gross, 0M~100M Only", x= "Rating Level", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())

#QQ-plot
qqnorm(newmovie$dlg, main = "QQ-Plot of Domestic Lifetime Gross")
qqline(newmovie$dlg, col = 'red')

```

As everyone can see, `dlg` has completely right-skewed distribution. 

# 2. Independent Variables EDA: Boxplots, Scatterplots, Correlation Test
### 2.1 SMART Question: Does rating affect to lifetime gross?
```{r}
# Scatterplot for imdbRating
ggplot(newmovie, aes(x=imdbRating, y=dlg))+
  geom_point()+
  geom_smooth(method=lm) +
  labs(title = "Scatter Plot for IMDB Rating", x="IMDB Rating", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())

# Scatterplot for rtRating
ggplot(newmovie, aes(x=rtRating, y=dlg))+
  geom_point()+
  geom_smooth(method=lm) +
  labs(title = "Scatter Plot for Rotten Tomatoes Rating", x="Rotten Tomatoes Rating", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())

# Correaltion between Rtaing and gross
cor.test(newmovie$imdbRating, newmovie$dlg)
cor.test(newmovie$rtRating, newmovie$dlg)

```

We did firstly Scatter plot to show intuitively how each rating affect to `dlg`. As you can see, it tends to have increasing linear relationship, but it should be looked into more. We did additional investigation by dividing the rating into 3 groups, which are 1 to 3.9, 4 to 7.9, and over 8.

#### 2.1.1 IMDB Rating
```{r echo=FALSE}
summary(newmovie$imdbRating)
sd(newmovie$imdbRating) 
```

```{r IMDB rating Plots}
# Histogram
ggplot(newmovie, aes(x=imdbRating)) +
  geom_histogram(binwidth = 0.1, color='darkblue', fill='lightblue') +
  labs(title = "Histogram of DLG by IMDB Rating", x="IMDB Rating", y="Frequency") +
  theme(plot.title = element_text(hjust = 0.5))

# Convert imdbRating into factor
imdbR_fac <- cut(newmovie$imdbRating, breaks = c(1, 3.9, 7.9, Inf), labels = paste("IMDB R ", 1:3, sep=""))

# Box-plot based on each IMDB Rating range without outliers
ggplot(newmovie, aes(x=imdbR_fac, y=dlg, fill=imdbR_fac)) +
  geom_boxplot(na.rm = T, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,250000000)) +
  labs(title = "Boxplot of Lifetime Gross by IMDB Rating", x= "IMDB Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())+
  scale_fill_discrete(name = "IMDB Rating", labels = c("1~3.9", "4~7.9", "8~ ")) +
  theme(legend.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("1~3.9", "4~7.9", "8~ "))
```
As the rating is subdivided, it can be seen that the higher the rating, the wider the range of the gross and the larger the gross.


#### 2.1.2 Rotten Tomatoes Rating
```{r tomato rating summary}
summary(newmovie$rtRating)
sd(newmovie$rtRating)
```

```{r Rotten Tomatoes Rating Plots}
# Histogram
ggplot(newmovie, aes(x=rtRating)) +
  geom_histogram(binwidth =2, color = 'darkblue', fill = 'lightblue') +
  labs(title = "Histogram of DLG by Rotten Tomatoes Rating", x="Rotten Tomatoes Rating", y="Frequency") +
  theme(plot.title = element_text(hjust = 0.5))


# Convert rtRating into factor
rtR_fac <- cut(newmovie$rtRating, breaks = c(-1, 39, 79, Inf), labels = paste("rt R ", 1:3, sep=""))

# Box-plot based on each rtRating range without outliers
ggplot(newmovie, aes(x=rtR_fac, y=dlg, fill=rtR_fac)) +
  geom_boxplot(na.rm = F, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,100000000)) +
  labs(title = "Boxplot of Lifetime Gross by rtRating", x= "Rotten Tomatoes Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())+
  scale_fill_discrete(name = "RT Rating", labels = c("0~39", "40~79", "80~ ")) +
  theme(legend.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("0~39", "40~79", "80~ "))
```
We did the same for the Rotten Tomatoes rating. However, the rt rating is not only that there is no difference in the gross, but even that tends to decline. 

What is interesting here is that if imdb rating is a full range of criticisms, including public, rt rating includes only expert and critic reviews. 

Think of it. It is not necessarily popular because it is a highly rated movie by movie critics.

### 2.2 SMART Question: Is there a difference in lifetime gross according to count? 
#### 2.2.1 Does count affect to lifetime gross?
```{r}

# Scatterplot for imdbCount
ggplot(newmovie, aes(x=imdbCount, y=dlg))+
  geom_point()+
  geom_smooth(method=lm)+
  labs(title = "Scatter Plot for IMDB Count", x="IMDB Count", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())


# Scatterplot for rtCount
ggplot(newmovie, aes(x=rtCount, y=dlg))+
  geom_point()+
  geom_smooth(method=lm)+
  labs(title = "Scatter Plot for Rotten Tomatoes Count", x="Rotten Tomatoes Count", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())


# Correaltion between imdbCount and gross
cor.test(newmovie$imdbCount, newmovie$dlg)
cor.test(newmovie$rtCount, newmovie$dlg)

```
In the case of `countRting`, there is a clear correlation with `dlg`.

### 2.3 SMART Question: Is there a difference in lifetime gross according to content rating? 
```{r}
#Convert contRating to factor
newmovie$contRating <- factor(newmovie$contRating, levels = c("G", "PG", "PG-13", "R", "NR", "NC17"))

```

```{r}
# Box-plot based on each contRating without outliers
ggplot(newmovie, aes(x=reorder(contRating,dlg,na.rm=T), y=dlg, fill=contRating)) +
  geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,200000000)) +
  labs(title = "Boxplot for Lifetime Gross by contRating", x= "Content Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  guides(fill = guide_legend(title = "Content Rating"))+
  scale_y_continuous(labels = label_number_si())
```

```{r}
# without NC17 & NR
noNC17NR <- subset (newmovie, contRating != "NC17" & contRating != "NR")

ggplot(noNC17NR, aes(x=reorder(contRating,dlg,na.rm=T), y=dlg, fill=contRating)) +
  geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,200000000)) +
  labs(title = "Boxplot for Lifetime Gross by contRating", x= "Content Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  guides(fill = guide_legend(title = "Content Rating"))+
  scale_y_continuous(labels = label_number_si())
```

As for content rating, movies that cover all ages or preschoolers tend to have a high gross as expected.

### 2.4 SMART Question: Is there a difference in lifetime gross according to year? 

```{r}
# Histogram
ggplot(newmovie, aes(x=year)) +
  geom_histogram(binwidth = 5, color = 'darkblue', fill = 'lightblue') +
  labs(title = "Histogram by Year", x="Year", y="Frequency") +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}

# Convert year to factor (1911~1929 / 1930~1949 / 1950~1969 / 1970~1989 / 1990~2009 / 2010~ )
newmovie$year <- cut(newmovie$year, breaks = c(1910, 1929, 1949, 1969, 1989, 2009, Inf), labels = paste("Year ", 1:6, sep=""))

# Box-plot based on each year without outliers
ggplot(newmovie, aes(x=year, y=dlg, fill=year)) +
  geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,115000000)) +
  labs(title = "Boxplot for Lifetime Gross by Year", x= "Year", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_discrete(name = "Year", labels = c("1911~1929", "1930~1949", "1950~1969", "1970~1989", "1990~2009", "2010~ ")) +
  theme(legend.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("1911~1929", "1930~1949", "1950~1969", "1970~1989", "1990~2009", "2010~ "))+
  scale_y_continuous(labels = label_number_si())


```

In order to find out the effect of each year, `year` is also grouped by 20 years.

What is interesting about `year` variable was that the gross tend to decrease over time.

### Correlation Matrix
```{r}
# Subset only numerical variables
num_newmovie <- movie[-c(1:5)]
str(num_newmovie)

# Correlation Matrix
corrnewmovie <- cor(num_newmovie, use = "complete.obs")
corrnewmovie

loadPkg("corrplot")
corrplot.mixed(corrnewmovie)
```
```{r}
lm1 <- lm(dlg~imdbCount, data = num_newmovie)
summary(lm1)
```
```{r}
lm2 <- lm(dlg~imdbCount+rtCount, data = num_newmovie)
summary(lm2)
```
```{r}
lm3 <- lm(dlg~imdbCount+rtCount+contRating, data = newmovie)
summary(lm3)
```