---
title: "Final data cleaning"
author: "C. Krall"
date: '2022-11-23'
output: html_document
---

```{r include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
```


```{r}
movie <- read.csv("movies.csv")
```

## Getting rid of the unnecessary columns
```{r}
movie_red <-
  movie %>%
  select(X, movie_title, content_rating, genres.x, runtime, tomatometer_status, tomatometer_rating, tomatometer_count, lifetime_gross, year, averageRating, numVotes) %>%
  rename(genre = genres.x, imbdRating = averageRating)
```


## Adding indicator variables for Genre

The first thing we need to do is find which genres are the most common. I created indicator variables for the top genres and summarizes their count
```{r}
movie_red <-
  movie_red %>%
  mutate(comedy = ifelse(str_detect(genre, "Comedy"), 1,0),
         horror = ifelse(str_detect(genre, "Horror"), 1,0),
         action = ifelse(str_detect(genre, "Action"), 1,0),
         drama = ifelse(str_detect(genre, "Drama"), 1,0),
         scifi = ifelse(str_detect(genre, "Science Fiction"), 1,0),
         arthouse = ifelse(str_detect(genre, "Art House"), 1,0),
         documentary = ifelse(str_detect(genre, "Documentary"), 1,0))

movie_red %>%
  count(comedy)
movie_red %>%
  count(horror)
movie_red %>%
  count(action)
movie_red %>%
  count(drama)
movie_red %>%
  count(scifi)
movie_red %>%
  count(arthouse)
movie_red %>%
  count(documentary)
```
drama comedy action

Based on the counts above, the biggest genre categories are drama, comedy, and action, so we will attempt to predict these genres.

## Making Indicators for Tomatoer Status
```{r}
movie_red <-
  movie_red %>%
  mutate(rotten = ifelse(str_detect(tomatometer_status, "Rotten"), 1, 0),
         fresh = ifelse(str_detect(tomatometer_status, "^Fresh"), 1, 0),
         cert_fresh = ifelse(str_detect(tomatometer_status, "Certified"), 1, 0),)
```





















