---
title: "Final- IMDB modeling"
author: "Tara"
date: "2022-11-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
```


```{r}
movie <- read.csv("movies.csv")
```

## Getting rid of the unnecessary columns
```{r}
movie_red <-
  movie %>%
  select(X, movie_title, content_rating, genres.x, runtime, tomatometer_status, tomatometer_rating, tomatometer_count, lifetime_gross, year, averageRating, numVotes) %>%
  rename(genre = genres.x, imdbRating = averageRating)

str(movie_red)
```

## Renaming genres to have generic names
```{r}
movie_red <-
  movie_red %>%
  mutate(genre = case_when(
    str_detect(genre, "Comedy") ~ "Comedy",
    str_detect(genre, "Horror")  ~ "Horror",
    str_detect(genre, "Action") ~ "Action",
    str_detect(genre, "Drama")  ~ "Drama",
    str_detect(genre, "Science Fiction") ~ "Science Fiction",
    str_detect(genre, "Art House")  ~ "Art House",
    str_detect(genre, "Documentary") ~ "Documentary",
    TRUE ~ genre
    )
  )

str(movie_red)

```

## Filtering down to only most common genres
```{r}


new_mov <- movie_red%>%filter(str_detect(genre,"Comedy|Action|Horror|Drama|Science Fiction|Art House|Documentary"))

str(new_mov)

```

## Creating factor variables
```{r}

new_mov$tomatometer_status <- as.factor(new_mov$tomatometer_status)
new_mov$content_rating <- as.factor(new_mov$content_rating)
new_mov$genre <- as.factor(new_mov$genre)

str(new_mov)
```

## Feature Selection 
```{r}

library("leaps")
reg.best10 <- regsubsets(imdbRating~runtime+tomatometer_status+tomatometer_rating+tomatometer_count+lifetime_gross+year+numVotes, data = new_mov, nvmax = 8, nbest = 2, method = "exhaustive")  # 
plot(reg.best10, scale = "adjr2", main = "Adjusted R^2")
plot(reg.best10, scale = "bic", main = "BIC")
plot(reg.best10, scale = "Cp", main = "Cp")
summary(reg.best10)
```
## Five Models based on feature selection & ANOVA


```{r results='markup'}
#top 4 numerical variables
fit1<- lm(imdbRating~runtime+tomatometer_count+year+tomatometer_status, data=new_mov)
summary(fit1)

#top 5 numerical variables
fit2<- lm(imdbRating~runtime+tomatometer_count+year+tomatometer_status+numVotes, data=new_mov)
summary(fit2)


#adding content rating
fit3<-lm(imdbRating~runtime+tomatometer_count+year+tomatometer_status+numVotes+content_rating, data=new_mov)
summary(fit3)

#adding genre
fit4<-lm(imdbRating~runtime+tomatometer_count+year+tomatometer_status+numVotes+genre, data=new_mov)
summary(fit4)

#adding genre and content rating
fit5<-lm(imdbRating~runtime+tomatometer_count+year+tomatometer_status+numVotes+genre+content_rating, data=new_mov)
summary(fit5)

anova(fit1, fit2, fit3, fit4, fit5)

```


Out of the 5 models, based on ANOVA test, the 2nd and 4th model are the best with the lowest p-value. When looking at the $R^2$ values, model 4 is the best at .369. Model 5 is slightly better at .37, but the p-value isn't as low, making model 4 the best out of the 5 models. 

