---
title: "Final- IMDB modeling"
author: "Tara"
date: "2022-11-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
```

## Getting rid of the unnecessary columns


```{r}
movie <- read.csv("movies.csv")
```

```{r}
movie_red <-
  movie %>%
  select(X, movie_title, content_rating, genres.y, runtime, tomatometer_status, tomatometer_rating, tomatometer_count, lifetime_gross, startYear, averageRating, numVotes) %>%
  rename(genre = genres.y, imdbRating = averageRating)
```


```{r}

ggplot(movie_red, aes(x=imdbRating)) + 
  geom_histogram(color="blue", fill="blue") + labs(title="IMDB histogram plot", x="IMDB Rating", y = "Count")
```

```{r}
library("ezids")
summaryIR <- summary(movie_red$imdbRating)
xkabledply(as.table(summaryIR), title = "Summary of IMDB Rating", wide = T)
```

## Rought count of genres 
Rough since this would not exactly count the unique genres as say 'Comedy' and 'comedy' woudl be counted seperatly  
```{r}
movie_red %>% 
   separate_rows(genre,sep=",") %>% 
   count(genre) %>%
   arrange(desc(n))
```

## Adding indicator variables for Genre

The first thing we need to do is find which genres are the most common. I created indicator variables for the top genres and summarizes their count
```{r}
movie_red <-
  movie_red %>%
  mutate(drama = ifelse(str_detect(genre, "Drama"), 1,0),
         comedy = ifelse(str_detect(genre, "Comedy"), 1,0),
         romance = ifelse(str_detect(genre, "Romance"), 1,0),
         crime = ifelse(str_detect(genre, "Crime"), 1,0),
         action = ifelse(str_detect(genre, "Action"), 1,0),
         adventure = ifelse(str_detect(genre, "Adventure"), 1,0),
         thriller = ifelse(str_detect(genre, "Thriller"), 1,0),
         documentary = ifelse(str_detect(genre, "Documentary"), 1,0),
         horror = ifelse(str_detect(genre, "Horror"), 1,0),
         biography = ifelse(str_detect(genre, "Biography"), 1,0),
         mystery = ifelse(str_detect(genre, "Mystery"), 1,0),
         scifi = ifelse(str_detect(genre, "Sci-Fi"), 1,0))
```


## Creating factor variables
```{r}

movie_red$tomatometer_status <- as.factor(movie_red$tomatometer_status)
movie_red$content_rating <- as.factor(movie_red$content_rating)
movie_red$comedy <- as.factor(movie_red$comedy)
movie_red$action <- as.factor(movie_red$action)
movie_red$scifi <- as.factor(movie_red$scifi)
movie_red$documentary <- as.factor(movie_red$documentary)
movie_red$drama <- as.factor(movie_red$drama)
movie_red$horror <- as.factor(movie_red$horror)
movie_red$romance <- as.factor(movie_red$romance)
movie_red$crime <- as.factor(movie_red$crime)
movie_red$adventure <- as.factor(movie_red$adventure)
movie_red$mystery <- as.factor(movie_red$mystery)
movie_red$biography <- as.factor(movie_red$biography)
movie_red$thriller <- as.factor(movie_red$thriller)





str(movie_red)
```

## Feature Selection 
```{r}
movie_red2 <-
  movie_red %>%
  select(-X, -movie_title, -genre)

library("leaps")
reg.best10 <- regsubsets(imdbRating~., data = movie_red2, nbest = 2, method = "exhaustive")  
plot(reg.best10, scale = "adjr2", main = "Adjusted R^2")
plot(reg.best10, scale = "bic", main = "BIC")
summary(reg.best10)
```
## Three Models based on feature selection & ANOVA


```{r}

#top numerical variables:
fit1<- lm(imdbRating~runtime+tomatometer_count+numVotes, data=movie_red)
summary(fit1)

#top variables with genre: runtime, tomato meter count, numVotes, drama, comedy, horror, biography

fit2<-lm(imdbRating~runtime+tomatometer_count+numVotes+drama+comedy+horror+biography, data=movie_red)
summary(fit2)


#adding qual vars- content rating and tomatometer_count
fit3<-lm(imdbRating~runtime+tomatometer_count+tomatometer_status+numVotes+content_rating, data=movie_red)
summary(fit3)

#top variables with genre: runtime, tomato meter count, numVotes, drama, comedy, horror, biography
fit4<-lm(imdbRating~runtime+tomatometer_count+tomatometer_status+numVotes+content_rating+drama+comedy+horror+biography, data=movie_red)
summary(fit4)


anova(fit1, fit2, fit3, fit4)

```


The ANOVA test indicates that the increases in variance between the models are signficant with very low p-values. This can be confirmed by looking at the p-values for each model, being less than .05. However, when looking at the $R^2$ values, the 4th model accounts for .358 of the variance, which is much higher than the other models.

