---
title: "Midterm Summary Paper"
author: "Tara, Yoni, Caroline, Arjun"
date: "2022-10-23"
output:
  prettydoc::html_pretty:
    theme: cayman
    number_sections: false
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'

---

```{r init, include=FALSE}

knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scientific=T, digits = 3) 

```

# Box Office Performance in the US

## Chapter 1: Introduction

Movies have always been a popular form of entertainment, but what makes a movie successful? The literature states multiple different factors that can influence box office sales. Most revolve around Oscar nominations, specific genres, and the directors/actors' popularity (Scott 2022). One less researched avenue in the literature was rating reviews. The information that was publicly available for use led us to utilize datasets from IMDB and Rotten Tomatoes, very popular movie rating websites. The datasets from these sites will allow analysis in the ratings review space. 


## Chapter 2: Description of the Data


### 2.1 Source Data

We combined three different datasets, IMDB, Rotten Tomatoes, and Box Office Mojo to create our master dataset to answer the SMART question: What factors affect box office performance sales in the US? The IMDB dataset is publicly available online, the Rotten Tomato dataset was pulled from Kaggle, and the Box Office Mojo dataset was obtained from Data World. We joined these datasets through an inner join on movie title, where the year of release ranged from 1912 to 2022. Due to the nature of combining three different datasets, there were multiple columns that were irrelevant to answering our SMART question. After removing those columns, we were left with 8 features to predict our target variable, domestic lifetime gross.  


The total number of observations for dataset consists of 7,981 observations with 9 variables. 

```{r ch2.1, include=FALSE}
library(ezids)
library(dplyr)

movie.red<- read.csv("movie_reduced.csv")
structure <- str(movie.red)


```


The features we used to determine box office performance were: 

-Movie title
-Content rating: G, PG, PG-13, R
-Year of Release
-Runtime
-IMDB rating: from 1-10
-IMDB count:  the number of votes that went into the IMDB rating 
-Rotten Tomato Rating: from 1-100
-Rotten Tomato Count: the number of professional votes that went into the Rotten Tomato rating


## Chapter 3: Exploratory Data Analysis

```{r clean, include=F}
movie.red$runtime <- as.numeric(movie.red$runtime)

movie_num <-
  movie.red %>%
  select(-1, -2)

movie_num <- na.omit(movie_num)
```


### Statistics Summary

```{r ezids, echo=FALSE, results=T}

xkablesummary(movie_num)


```











## Model Fitting: Goals and Overview
```{r na remove, include=FALSE}
movie.red<- na.omit(movie.red)
```

We fit several models with the goal of finding which combination of predictors worked best for predicting domestic lifetime gross. Out initial strategy was to use a correlation plot and forward selection to find the best combination of numerical predictors. Then, due to our finding in the EDA process, we added content rating to the best model to see if that improved model performance. We found that the best model included number of IMDb ratings, number of Rotten Tomatos ratings, and Content Rating as predictors for domestic lifetime gross. It is worth noting that during the EDA process, we did discover that several model conditions were not being met in particular the normality assumption. However, because our somple size is so large, we still proceeded to fit these linear models. 


## Model Results Summary and Interpretations
Model 1: Lifetime Gross = bo + b1xIMDbCount
  H0: b1 = 0 (IMDb count has no significant effect on Lifetime gross)
  Ha: b1 != 0 (There is some effect)
  
```{r lm1, results='markup'}
lm1 <- lm(dlg~imdbCount, data = movie.red)
summary(lm1)
```

The t-statistic for the coefficient on imdbCount is 67.63, which gives a p-value of approximately 0. Therefore we can reject the null hypothesis and conclude that there is strong evidence that imdbCount has a positive relationship with lifetime gross.

Model 2: Lifetime Gross = bo + b1xIMDbCount + b2xRTCount
  H0: b2 = 0 (Rotten Tomato count has no significant effect on Lifetime gross)
  Ha: b2 != 0 (There is some effect)
  
```{r lm2, results='markup'}
lm2 <- lm(dlg~imdbCount+rtCount, data = movie.red)
summary(lm2)
```

The t-statistic for the coefficient on rtCount is 29.16. This gives a p-value of approximately 0. Therefore, there is strong evidence that the number of rotten tomatoes reviews has a statistically significant positive relationship with domestic lifetime gross.

Model 3: Lifetime Gross = bo + b1xIMDbCount + b2xRTCount + b3xruntime
  H0: b3 = 0 (Runtime has no significant effect on Lifetime gross)
  Ha: b3 != 0 (There is some effect)

```{r lm3, results='markup'}
lm3 <- lm(dlg~imdbCount+rtCount+runtime, data = movie.red)
summary(lm3)
```

The t-statistic for runtime is 1.834, which gives a p-value of 0.0667. There is no evidence that there is a statistically significant relationship between runtime and domestic lifetime gross. For this reason, we rejected this predictor from our model.

ANOVA: Models 1, 2, & 3
```{r anova, results='markup'}
anova(lm3, lm2, lm1)
```

The F-statistic comparing models 2 and 3 is 3.363, which gives a p-value of 0.0667. Therefore there is no evidence that model 3 is performing significantly better than model 2, therefore we rejected model 3. The F-statistic comparing models 1 and 2 is 850.7, which gives a p-value of approximately 0. Therefore, there is strong evidence that model 2 performs better than model 1, therfore we accepted model 2 as our best model.

Model 4: Lifetime Gross = bo + b1xIMDbCount + b2xRTCount + *b3*XcontentRating
  H0: all b3i = 0, where i represents the levels of content rating (content rating has no significant effect on Lifetime gross)
  Ha: some b3i != 0 (Some level of content rating has an effect)
  
```{r content rating lm, results='markup'}
lm4 <- lm(dlg~imdbCount+rtCount+contRating, data = movie.red)
summary(lm4)

```

The coefficients for all ratings have p-values of approximately 0. For this reason, we can reject our null hypothesis and say that at least one coefficient for content rating is not zero. There is strong evidence that content rating has a statisitically significant relationship with domestic lifetime gross. 

ANOVA: Models 2 & 4
```{r anova cont rating, results='markup'}
anova(lm4, lm2)
```

The F-statistic for comparing models 2 and 4 is 118.41, which gives a p-value of approximately 0. Therefore there is strong evidence that model 4, which includes content rating, is performing statistically significantly better than model 2. We selected model 4 as our final model.

###Conclusion

## Model Conclusions
Our model illustrates that the number of reviews on both rotten tomatoes and IMDb, along with content rating, are the best combinations of variables to predict domestic lifetime gross (R^2= 0.4693). We can generally say that popularity of the movie is more important than the extent to which it is critically acclaimed. Even if it is considered 'bad' by critics, if enough people are talking about it on these online platforms, it can expect to make money either way. In addition, as the movie's rating gets more restrictive, it can expect to make less money. This also intuitively made sense to us, as children and teens make up a large portion of movie audiences. If this part of the population is unable to go see certain films, like those rated R, this will be reflected in slightly lower box office sales. Another factor which could impact this is that big, high earning blockbuster films, like super hero movies, tend to have a lower rating of either G or PG so that children can see them in theaters.


### Limitations

The main goal when analyze data and drawing conclusions is to have a sample representative of the given population. We should be able to infer the population based on our analysis of the sample. Although we used data from two very popular rating sites, we must acknowledge that there are many more rating sites that people use to rate movies. The issue in using these various sites was that the data was either unavailable without a fee or was very incomplete, which could skew our data. We thought it would be best to use the most complete data from two popular rating websites. In doing so, we also acknowledge that this may not be the most representative sample. Although, with close to 8,000 observations, this is still a robust dataset. 


### Future Research

There are many avenues for future research to be explored. Within the scope of this class, we can re-analyze the data while accounting for inflation throughout the years. Considering the year of release spanning 110 years, the rate of inflation could alter the results quite drastically. In the same realm, we can analyze the data through time series, especially during the pandemic from 2019-2022, and how that affected box office sales. Around this time, streaming platforms also became increasingly popular since many people were in lockdown, which negatively impacted box office sales. 





## Bibliography

Scott, G. Determinants of box office performance: Return of the regressions. Retrieved October 28, 2022, from https://scholarworks.uni.edu/cgi/viewcontent.cgi?article=1143&amp;context=mtie 