---
title: "Midterm code compiled"
author: "Arjun, Caroline, Yoni, Tara"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---


```{r init, include=FALSE}

knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scientific=T, digits = 3) 

```

## Reduced Dataset

Importing the existing consolidated dataset.
```{r Dataset}
filepath = "movies.csv"
movie <- read.csv(filepath)
head(movie)
```
## Subsetting

Listing all columns in the dataset.
```{r subsetting, include=FALSE}
colnames(movie)
```

Columns we are interested in:  
_format : original col name : new col name - description_

1. __primaryTitle__ : __title__ - The title of  the movie. _(source: IMDB)_
2. __content_rating__ : __contRating__- The category based on the movie suitability for audience. _(source: Rotten Tomatoes)_
3. __startYear__ : __year__ - The year of movie release. _(source: IMDB)_
4. __runtimeMinutes__ : __runtime__ - The movie run time in minutes. _(source: IMDB)_
5. __averageRating__ : __imdbRating__-  The IMDB rating, average of user votes. _(source: IMDB)_
6. __numVotes__ : __imdbCount__ - The number of votes that went into the IMDB rating. _(source: IMDB)_
7. __tomatometer_rating__ : __rtRating__ - The percentage of positive critic reviews. _(source: Rotten Tomatoes)_
8. __tomatometer_count__ : __rtCount__- The number of critic ratings counted for tomatometer rating. _(source: Rotten Tomatoes)_
9. __lifetime_gross__ : __dlg__-  The domestic lifetime gross of the movie in USD (not accounting inflation). _(source: Box Office Mojo)_


```{r titles}
vars <- c("primaryTitle","content_rating","startYear","runtimeMinutes","averageRating","numVotes","tomatometer_rating","tomatometer_count","lifetime_gross") #list of org col names
nvars <- c("title","contRating","year","runtime","imdbRating","imdbCount","rtRating","rtCount","dlg") #list of new col names

movie.red <- movie[vars] #creating new df with only cols in vars
colnames(movie.red) <- nvars #renaming using nvars

head(movie.red)
```
```{r export}
#exporting to csv
write.csv(movie.red,"movie_reduced.csv")
```
Importing datasets and necessary packages
```{r inlcue=FALSE}
#Importing Datasets
movie <- read.csv("movie_reduced.csv")
str(movie)
summary(movie)

newmovie <- na.omit(movie)
summary(newmovie)

```

```{r include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ezids)
library(scales)
loadPkg("gridExtra")

knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scipen=999)
```

--------------------------------------------------------------------------
# 1. Independent Variables EDA: Overview of Data
### 1.1 Overview for Domestic Lifetime Gross 

```{r include=FALSE}
summary(newmovie$dlg)
sd(newmovie$dlg)

```


Refined dataset yields following observations for the domestic lifetime gross of ranked movies: the minimum price is $`r min(movie$dlg)` and the maximum price is $`r max(movie$dlg)`; the mean of gross is $`r mean(movie$dlg)` (indicating mean is higher than median ($`r median(movie$dlg)`) which means the shape of distribution is right-skewed); the standard deviation of gross is $`r sd(movie$dlg)`.

x="Gross of Movie ($)",   xlim (NA, 100000000)  +
```{r Plots for dlg}
# Histogram
ggplot(newmovie, aes(x=dlg)) + 
  geom_histogram(col='dark blue', fill='light blue', bins = 30) + 
  labs(title = "Histogram of Domestic Lifetime Gross, 0M~100M Only",  y="Frequency") + 
  theme(plot.title = element_text(hjust = 0.5))+
  scale_x_continuous("Gross of Movie($)", limits= c(NA, 100000000), labels = label_number_si())

#Boxplot
ggplot(newmovie, aes(y=dlg)) +
  geom_boxplot(na.rm = T, colour="sky blue", outlier.colour="dark blue", outlier.shape=8, outlier.size=4) +
  coord_cartesian(ylim = c(0,100000000)) +
  labs(title = "Boxplot of Domestic Lifetime Gross, 0M~100M Only", x= "Rating Level", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())

#QQ-plot
qqnorm(newmovie$dlg, main = "QQ-Plot of Domestic Lifetime Gross")
qqline(newmovie$dlg, col = 'red')

```

As everyone can see, `dlg` has completely right-skewed distribution. 

# 2. Independent Variables EDA: Boxplots, Scatterplots, Correlation Test
### 2.1 SMART Question: Does rating affect to lifetime gross?
```{r}
# Scatterplot for imdbRating
ggplot(newmovie, aes(x=imdbRating, y=dlg))+
  geom_point()+
  geom_smooth(method=lm) +
  labs(title = "Scatter Plot for IMDB Rating", x="IMDB Rating", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())

# Scatterplot for rtRating
ggplot(newmovie, aes(x=rtRating, y=dlg))+
  geom_point()+
  geom_smooth(method=lm) +
  labs(title = "Scatter Plot for Rotten Tomatoes Rating", x="Rotten Tomatoes Rating", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())

# Correaltion between Rtaing and gross
cor.test(newmovie$imdbRating, newmovie$dlg)
cor.test(newmovie$rtRating, newmovie$dlg)


```

We did firstly Scatter plot to show intuitively how each rating affect to `dlg`. As you can see, it tends to have increasing linear relationship, but it should be looked into more. We did additional investigation by dividing the rating into 3 groups, which are 1 to 3.9, 4 to 7.9, and over 8.

#### 2.1.1 IMDB Rating
```{r echo=FALSE}
summary(newmovie$imdbRating)
sd(newmovie$imdbRating) 
```

```{r IMDB rating Plots}
# Histogram
ggplot(newmovie, aes(x=imdbRating)) +
  geom_histogram(binwidth = 0.1, color='darkblue', fill='lightblue') +
  labs(title = "Histogram of DLG by IMDB Rating", x="IMDB Rating", y="Frequency") +
  theme(plot.title = element_text(hjust = 0.5))

# Convert imdbRating into factor
imdbR_fac <- cut(newmovie$imdbRating, breaks = c(1, 3.9, 7.9, Inf), labels = paste("IMDB R ", 1:3, sep=""))

# Box-plot based on each IMDB Rating range without outliers
ggplot(newmovie, aes(x=imdbR_fac, y=dlg, fill=imdbR_fac)) +
  geom_boxplot(na.rm = T, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,250000000)) +
  labs(title = "Boxplot of Lifetime Gross by IMDB Rating", x= "IMDB Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())+
  scale_fill_discrete(name = "IMDB Rating", labels = c("1~3.9", "4~7.9", "8~ ")) +
  theme(legend.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("1~3.9", "4~7.9", "8~ "))
```
As the rating is subdivided, it can be seen that the higher the rating, the wider the range of the gross and the larger the gross.


#### 2.1.2 Rotten Tomatoes Rating
```{r tomato rating summary}
summary(newmovie$rtRating)
sd(newmovie$rtRating)
```

```{r Rotten Tomatoes Rating Plots}
# Histogram
ggplot(newmovie, aes(x=rtRating)) +
  geom_histogram(binwidth =2, color = 'darkblue', fill = 'lightblue') +
  labs(title = "Histogram of DLG by Rotten Tomatoes Rating", x="Rotten Tomatoes Rating", y="Frequency") +
  theme(plot.title = element_text(hjust = 0.5))


# Convert rtRating into factor
rtR_fac <- cut(newmovie$rtRating, breaks = c(-1, 39, 79, Inf), labels = paste("rt R ", 1:3, sep=""))

# Box-plot based on each rtRating range without outliers
ggplot(newmovie, aes(x=rtR_fac, y=dlg, fill=rtR_fac)) +
  geom_boxplot(na.rm = F, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,100000000)) +
  labs(title = "Boxplot of Lifetime Gross by rtRating", x= "Rotten Tomatoes Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())+
  scale_fill_discrete(name = "RT Rating", labels = c("0~39", "40~79", "80~ ")) +
  theme(legend.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("0~39", "40~79", "80~ "))
```
We did the same for the Rotten Tomatoes rating. However, the rt rating is not only that there is no difference in the gross, but even that tends to decline. 

What is interesting here is that if imdb rating is a full range of criticisms, including public, rt rating includes only expert and critic reviews. 

Think of it. It is not necessarily popular because it is a highly rated movie by movie critics.

### 2.2 SMART Question: Is there a difference in lifetime gross according to count? 
#### 2.2.1 Does count affect to lifetime gross?
```{r}

# Scatterplot for imdbCount
ggplot(newmovie, aes(x=imdbCount, y=dlg))+
  geom_point()+
  geom_smooth(method=lm)+
  labs(title = "Scatter Plot for IMDB Count", x="IMDB Count", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())


# Scatterplot for rtCount
ggplot(newmovie, aes(x=rtCount, y=dlg))+
  geom_point()+
  geom_smooth(method=lm)+
  labs(title = "Scatter Plot for Rotten Tomatoes Count", x="Rotten Tomatoes Count", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number_si())


# Correaltion between imdbCount and gross
cor.test(newmovie$imdbCount, newmovie$dlg)
cor.test(newmovie$rtCount, newmovie$dlg)

```
In the case of `countRting`, there is a clear correlation with `dlg`.

### 2.3 SMART Question: Is there a difference in lifetime gross according to content rating? 
```{r}
#Convert contRating to factor
newmovie$contRating <- factor(newmovie$contRating, levels = c("G", "PG", "PG-13", "R", "NR", "NC17"))

```

```{r}
# Box-plot based on each contRating without outliers
ggplot(newmovie, aes(x=reorder(contRating,dlg,na.rm=T), y=dlg, fill=contRating)) +
  geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,200000000)) +
  labs(title = "Boxplot for Lifetime Gross by contRating", x= "Content Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  guides(fill = guide_legend(title = "Content Rating"))+
  scale_y_continuous(labels = label_number_si())
```

```{r}
# without NC17 & NR
noNC17NR <- subset (newmovie, contRating != "NC17" & contRating != "NR")

ggplot(noNC17NR, aes(x=reorder(contRating,dlg,na.rm=T), y=dlg, fill=contRating)) +
  geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,200000000)) +
  labs(title = "Boxplot for Lifetime Gross by contRating", x= "Content Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  guides(fill = guide_legend(title = "Content Rating"))+
  scale_y_continuous(labels = label_number_si())
```

As for content rating, movies that cover all ages or preschoolers tend to have a high gross as expected.

### 2.4 SMART Question: Is there a difference in lifetime gross according to year? 

```{r}
# Histogram
ggplot(newmovie, aes(x=year)) +
  geom_histogram(binwidth = 5, color = 'darkblue', fill = 'lightblue') +
  labs(title = "Histogram by Year", x="Year", y="Frequency") +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}

# Convert year to factor (1911~1929 / 1930~1949 / 1950~1969 / 1970~1989 / 1990~2009 / 2010~ )
newmovie$year <- cut(newmovie$year, breaks = c(1910, 1929, 1949, 1969, 1989, 2009, Inf), labels = paste("Year ", 1:6, sep=""))

# Box-plot based on each year without outliers
ggplot(newmovie, aes(x=year, y=dlg, fill=year)) +
  geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,115000000)) +
  labs(title = "Boxplot for Lifetime Gross by Year", x= "Year", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_discrete(name = "Year", labels = c("1911~1929", "1930~1949", "1950~1969", "1970~1989", "1990~2009", "2010~ ")) +
  theme(legend.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("1911~1929", "1930~1949", "1950~1969", "1970~1989", "1990~2009", "2010~ "))+
  scale_y_continuous(labels = label_number_si())


```

In order to find out the effect of each year, `year` is also grouped by 20 years.

What is interesting about `year` variable was that the gross tend to decrease over time.




```{r clean}
movie.red$runtime <- as.numeric(movie.red$runtime)

movie_num <-
  movie.red %>%
  select(-1, -2)

movie_num <- na.omit(movie_num)
```

## Corrplot

```{r corplot, echo=FALSE}
corm <- cor(movie_num)
corrplot::corrplot(corm)
```


## Statistics Summary

```{r ezids, results='markup'}


xkablesummary(movie_num)


```


## Models 

Based on the correlation matrix of the numerical variables, the first feature we chose to run a regression on was imdbCount. After running this model, we got an R^2 value of 0.3771, which is not bad, but could certainly be improved upon. Both the intercept term and the coefficient for IMDb count are highly significant. As number of IMDb ratings increase by 1, the domestic lifetime gross increases by 219USD.


```{r lm1, results='markup'}
lm1 <- lm(dlg~imdbCount, data = movie_num)
summary(lm1)
```

In order to see if we  could improve the R^2 value, we added the explanatory variable with the next highest correlation with domestic lifetime groos, which is Rotten Tomatos review count. This model increases he R^2 value to 0.4372, which for non-scientific data is fairly decent. Both coefficients are highly significant in the model. When running a one way ANOVA for this model andour original model, we get an F-stat of 838.3 (p value approx 0), which means model 2 is performing much better than the reduced model. 

```{r lm2, results='markup'}
lm2 <- lm(dlg~imdbCount+rtCount, data = movie_num)
summary(lm2)
```

Following the same logic as with model two, we added runtime as a third explanatory variable. This coefficient is not significant in the model and has no impact on the R^2 value. Running a one way ANOVA confirms that model 3 does not perform better than model 2 (p value=0.171), so Model 2 is our best model using only numerical variables.

```{r lm3, results='markup'}
lm3 <- lm(dlg~imdbCount+rtCount+runtime, data = movie_num)
summary(lm3)
```

## ANOVA

```{r anova, results='markup'}
anova(lm3, lm2)
anova(lm2, lm1)
```

## Content Rating

```{r content rating lm, results='markup'}
lm4 <- lm(dlg~imdbCount+rtCount+contRating, data = movie.red)
summary(lm4)

```


