---
title: "Reduced Dataset"
author: "Arjun Bigly"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reduced Dataset

Importing the existing consolidated dataset.
```{r}
filepath = "movies.csv"
movie <- read.csv(filepath)
head(movie)
```
## Subsetting

Listing all columns in the dataset.
```{r}
colnames(movie)
```

Columns we are interested in:  
_format : original col name : new col name - description_

1. __primaryTitle__ : __title__ - The title of  the movie. _(source: IMDB)_
2. __content_rating__ : __contRating__- The category based on the movie suitability for audience. _(source: Rotten Tomatoes)_
3. __startYear__ : __year__ - The year of movie release. _(source: IMDB)_
4. __runtimeMinutes__ : __runtime__ - The movie run time in minutes. _(source: IMDB)_
5. __averageRating__ : __imdbRating__-  The IMDB rating, average of user votes. _(source: IMDB)_
6. __numVotes__ : __imdbCount__ - The number of votes that went into the IMDB rating. _(source: IMDB)_
7. __tomatometer_rating__ : __rtRating__ - The percentage of positive critic reviews. _(source: Rotten Tomatoes)_
8. __tomatometer_count__ : __rtCount__- The number of critic ratings counted for tomatometer rating. _(source: Rotten Tomatoes)_
9. __lifetime_gross__ : __dlg__-  The domestic lifetime gross of the movie in USD (not accounting inflation). _(source: Box Office Mojo)_


```{r}
vars <- c("primaryTitle","content_rating","startYear","runtimeMinutes","averageRating","numVotes","tomatometer_rating","tomatometer_count","lifetime_gross") #list of org col names
nvars <- c("title","contRating","year","runtime","imdbRating","imdbCount","rtRating","rtCount","dlg") #list of new col names

movie.red <- movie[vars] #creating new df with only cols in vars
colnames(movie.red) <- nvars #renaming using nvars

head(movie.red)
```
```{r}
#exporting to csv
write.csv(movie.red,"movie_reduced.csv")
```

