---
title: "Logistic Regression for Genre"
author: "Nayaeun Kwon"
date: '2022-11-29'
output: html_document
---

```{r include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(purrr)
options(scipen = n)

```


```{r}
movie <- read.csv("movies.csv")
```

## Getting rid of the unnecessary columns
```{r}
movie_red <-
  movie %>%
  select(movie_title, content_rating, genres.y, runtime, tomatometer_rating, lifetime_gross, year, averageRating, numVotes) %>%
  rename(genre = genres.y, imbdRating = averageRating) %>%
  na.omit()

str(movie_red)

movie_red$content_rating <- as.factor(movie_red$content_rating)
str(movie_red)
```

```{r}
movie_red %>% 
   separate_rows(genre,sep=",") %>% 
   count(genre) %>%
   arrange(desc(n))
```

Drama, Comedy, Romance


## Adding indicator variables for Genre

The first thing we need to do is find which genres are the most common. I created indicator variables for the top genres and summarizes their count
```{r}
movie_red <-
  movie_red %>%
  mutate(drama = ifelse(str_detect(genre, "Drama"), 1,0),
         comedy = ifelse(str_detect(genre, "Comedy"), 1,0),
         romance = ifelse(str_detect(genre, "Romance"), 1,0),
)
```
drama comedy romance

Based on the counts above, the biggest genre categories are drama, comedy, and romance, so we will attempt to predict these genres.

```{r}
movieclean <- movie_red[, c('content_rating', 'runtime', 'tomatometer_rating', 'lifetime_gross', 'year', 'imbdRating', 'numVotes')]

colnames(movie_red)
```

# drama indicator variable into y variables
```{r}
movieclean$y = movie_red[,10]
movieclean$y <- as.factor(movieclean$y)
str(movieclean)
```

```{r}
library("leaps")
library("bestglm")

res.bestglm <-
  bestglm(Xy = movieclean,
          family = binomial(link = "logit"),
          IC = "AIC",
          method = "exhaustive")

res.bestglm$BestModels
dramaglm <- res.bestglm$BestModel
summary(dramaglm)
```
The best model has AIC 9827.668 with all variables, `content_rating`, `runtime`, `tomatometer_rating`, `lifeime_gross`, `year`, `imbdRating`, and `numVotes`.


```{r HosmerLemeshow}
library("ResourceSelection") 
dramaHoslem = hoslem.test(movieclean$y, fitted(dramaglm)) # Hosmer and Lemeshow test, a chi-squared test
dramaHoslem
```

The p-value of `r dramaHoslem$p.value` is relatively high. This indicates the model is not really a good fit, despite all the coefficients are significant.

# comedy indicator variable into y variables
```{r}
movieclean$y = movie_red[,11]
movieclean$y <- as.factor(movieclean$y)
str(movieclean)
```

```{r}
res.bestglm <-
  bestglm(Xy = movieclean,
          family = binomial(link = "logit"),
          IC = "AIC",
          method = "exhaustive")

res.bestglm$BestModels
comedyglm <- res.bestglm$BestModel
summary(comedyglm)
```
The best model has AIC 9623.153 with all variables exxcept `numVotes`.

```{r HosmerLemeshow}
comedyHoslem = hoslem.test(movieclean$y, fitted(comedyglm))
comedyHoslem
```

The p-value of `r comedyHoslem$p.value` is relatively high. This indicates the model is not really a good fit, despite all the coefficients are significant.

# romance indicator variable into y variables
```{r}
movieclean$y = movie_red[,12]
movieclean$y <- as.factor(movieclean$y)
str(movieclean)
```

```{r}
res.bestglm <-
  bestglm(Xy = movieclean,
          family = binomial(link = "logit"),
          IC = "AIC",
          method = "exhaustive")

res.bestglm$BestModels
romanceglm <- res.bestglm$BestModel
summary(romanceglm)
```
The best model has AIC 7270.020 with all variables, `content_rating`, `runtime`, `tomatometer_rating`, `lifeime_gross`, `year`, `imbdRating`, and `numVotes`.

```{r HosmerLemeshow}
romanceHoslem = hoslem.test(movieclean$y, fitted(romanceglm))
romanceHoslem
```

The p-value of `r romanceHoslem$p.value` is relatively high. This indicates the model is not really a good fit, despite all the coefficients are significant.

