---
title: "Box Office Performance "
author: "Arjun Bingly, Caroline Krall, Nayaeun Kwon, Tara Thomas"
date: "2022-10-23"
output:
  prettydoc::html_pretty:
    theme: cayman
    number_sections: false
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
---
```{r include=FALSE}
# Setting Environment 

library(dplyr)
library(tidyr)
library(ggplot2)
library(ezids)
library(scales)
loadPkg("corrplot")

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, fig.align = 'center', error = F, message = F)
options(scipen=999)
```



```{r include=F}
# Importing dataset 
filepath = "movies.csv" 
org_movie <- read.csv(filepath)
head(org_movie)
colnames(org_movie)

# Changing column name
vars <- c("primaryTitle","lifetime_gross","content_rating","year","runtimeMinutes","averageRating","tomatometer_rating","numVotes","tomatometer_count") 
# List of new col names
nvars <- c("Title","LifetimeGross","contentR","Year","Runtime","imdbR","rottentmtR","imdbC","rottentmtC") 

# Creating new df with only cols in vars
movie <- org_movie[vars] 
colnames(movie) <- nvars #renaming using nvars
head(movie)

# Exporting to csv
write.csv(movie,"movie_reduced.csv")
```


```{r include=F}
# Setting New Dataset
movie <- read.csv("movie_reduced.csv")
movie <- na.omit(movie)

movie <- subset(movie, select = -c(X) )

movie$Runtime <- as.numeric(movie$Runtime)
movie$contentR <- factor(movie$contentR, levels = c("G", "PG", "PG-13", "R", "NC17", "NR"))

summary(movie)
```

```{r echo=FALSE}
xkablesummary(movie)
```

Variable descriptions are as follows:
_format :_ __col name__ - _description_

1. __Title__ - The title of  the movie. _(source: IMDB)_
2. __LifetimeGross__ -  The domestic lifetime gross of the movie in USD (not accounting inflation). _(source: Box Office Mojo)_
3. __contentR__ - The category based on the movie suitability for audience. _(source: Rotten Tomatoes)_
4. __Year__ - The year of movie release. _(source: IMDB)_
5. __Runtime__ - The movie run time in minutes. _(source: IMDB)_
6. __imdbR__ -  The IMDB rating from 1 to 10, average of user votes. _(source: IMDB)_
7. __rottentmtR__ - The percentage of positive critic reviews from 1 to 100. _(source: Rotten Tomatoes)_
8. __imdbC__ - The number of votes that went into the IMDB rating. _(source: IMDB)_
9. __rottentmtC__ - The number of critic ratings counted for tomatometer rating. _(source: Rotten Tomatoes)_


# 3. Variable EDA: Slicing the Data for an Overview

```{r include=F}
summary(movie$LifetimeGross)
```


### 3.1 Independent Variable: __Lifetime Gross__ Overveiw

```{r include=F}
#Boxplot of Lifetime Gross
ggplot(movie, aes(y=LifetimeGross)) +
  geom_boxplot(na.rm = T, colour="sky blue", outlier.colour="dark blue", outlier.shape=8, outlier.size=4) +
  coord_cartesian() +
  labs(title = "Boxplot of Domestic Lifetime Gross", x= "Rating Level", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))

```

```{r}
# Histogram of Lifetime Gross
ggplot(movie, aes(x=LifetimeGross)) + 
  geom_histogram(col='black', fill='light blue', bins = 30) + 
  labs(title = "Histogram of Domestic Lifetime Gross") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=15))+
  scale_x_continuous("Lifetime Gross of Movie($)", labels = label_number(scale_cut = cut_short_scale()))+
  scale_y_continuous("Frequency")

# QQ plot of lifetime Gross
qqnorm(movie$LifetimeGross, main = "QQ-Plot of Domestic Lifetime Gross")
qqline(movie$LifetimeGross, col = 'blue')
```

### 3.2 Dependent Variable

#### 3.2.1 __Content rating__ overview

The descriptions for content rating we are dealing with are as follows: _format :_ __Content rating__ - _description_

1. __G__ - For all audience. _(source: IMDB)_
2. __PG__ -  Parental guidance suggested (mainly for under 10's). _(source: IMDB)_
3. __PG-13__ - Parental guidance suggested for children under 13. _(source: IMDB)_
4. __R__ - Under 17 not admitted without parent or guardian. _(source: IMDB)_
5. __NC17__ - Under 17 not admitted. _(source: IMDB)_
6. __NR__ - Not been submitted for a rating or an uncut version of movie. _(source: ATLAS CINEMAS)_

```{r}
# Barplot of content rating
ggplot(movie, aes(x=contentR, fill=contentR)) + 
  geom_bar(color='black')+
  labs(title="Barplot by Content Rating", x="Content Rating", y="Frequency", fill = "Content Rating")+
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size=15))

# Boxplot of content rating
ggplot(movie, aes(x=contentR, y=LifetimeGross, fill=contentR)) +
  geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,200000000)) +
  labs(title = "Boxplot of Lifetime Gross by Content Rating", x= "Content Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size=15))+
  guides(fill = guide_legend(title = "Content Rating"))+
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))
```

#### 3.2.2 __Year__ overview

```{r}
# Histogram of year
ggplot(movie, aes(x=Year)) +
  geom_histogram(col='black', fill='light blue', bins = 30) +
  labs(title = "Histogram by Year", x="Year", y="Frequency") +
  theme(plot.title = element_text(hjust = 0.5,face='bold', size=15))

# Convert year to factor (1980~1989 / 1990~1999 / 2000~2009 / 2010~ ) to figure out earning changing over time
year_fac <- cut(movie$Year, breaks = c(1979, 1989, 1999, 2009, Inf), labels = paste("Year ", 1:4, sep=""))

# Boxplot based on each year
ggplot(movie, aes(x=year_fac, y=LifetimeGross, fill=year_fac)) +
  geom_boxplot(na.rm = TRUE) +
  labs(title = "Boxplot of Lifetime Gross by Year", x= "Year", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5, face='bold', size=15))+
  scale_fill_discrete(name = "Year", labels = c("1980~1989", "1990~1999", "2000~2009", "2010~ ")) +
  theme(legend.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("1980~1989", "1990~1999", "2000~2009", "2010~ "))+
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))


# Boxplot based on each year without outliers
ggplot(movie, aes(x=year_fac, y=LifetimeGross, fill=year_fac)) +
  geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,95000000)) +
  labs(title = "Boxplot of Lifetime Gross by Year without Outliers", x= "Year", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5, face='bold', size=15))+
  scale_fill_discrete(name = "Year", labels = c("1980~1989", "1990~1999", "2000~2009", "2010~ ")) +
  theme(legend.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("1980~1989", "1990~1999", "2000~2009", "2010~ "))+
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))

```

#### 3.2.3 __IMDB rating__ overview

```{r include=FALSE}
summary(movie$imdbR)
sd(movie$imdbR) 
```

```{r}
# Histogram of IMDB rating
ggplot(movie, aes(x=imdbR)) + 
  geom_histogram(col='black', fill='light blue', binwidth = 0.1) + 
  labs(title = "Histogram of IMDB Rating") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=15))+
  scale_x_continuous("IMDB Rating", labels = label_number(scale_cut = cut_short_scale()))+
  scale_y_continuous("Frequency")+
  theme(plot.title = element_text(hjust = 0.5))

# Convert IMDB Rating into factor to figure out change of earning by rating range
imdbR_fac <- cut(movie$imdbR, breaks = c(1, 3.9, 7.9, Inf), labels = paste("IMDB R ", 1:3, sep=""))

# Boxplot based on each IMDB Rating range without outliers
ggplot(movie, aes(x=imdbR_fac, y=LifetimeGross, fill=imdbR_fac)) +
  geom_boxplot(na.rm = T, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,250000000)) +
  labs(title = "Boxplot of Lifetime Gross by IMDB Rating \n w/out outliers", x= "IMDB Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5, face='bold'))+
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))+
  scale_fill_discrete(name = "IMDB Rating", labels = c("1~3.9", "4~7.9", "8~ ")) +
  theme(legend.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("1~3.9", "4~7.9", "8~ "))
```


#### 3.2.4 __Rotten Tomatoes rating__ overview

```{r include=FALSE}
summary(movie$rottentmtR)
sd(movie$rottentmtR)
```

```{r}
# Histogram of rotten tomatoes rating
ggplot(movie, aes(x=rottentmtR)) +
  geom_histogram(binwidth =2, color = 'darkblue', fill = 'lightblue') +
  labs(title = "Histogram of Rotten Tomatoes Rating", x="Rotten Tomatoes Rating", y="Frequency") +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))


# Convert rottentmtR into factor to figure out the change of earning by rotten tomatoes rating
rtR_fac <- cut(movie$rottentmtR, breaks = c(-1, 39, 79, Inf), labels = paste("rt R ", 1:3, sep=""))

# Boxplot based on each rtRating range without outliers
ggplot(movie, aes(x=rtR_fac, y=LifetimeGross, fill=rtR_fac)) +
  geom_boxplot(na.rm = F, outlier.shape = NA) +
  coord_cartesian(ylim = c(0,100000000)) +
  labs(title = "Boxplot of Lifetime Gross by Rotten Tomatoes Rating \n w/out outliers", x= "Rotten Tomatoes Rating", y= "Domestic Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size =15))+
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))+
  scale_fill_discrete(name = "RT Rating", labels = c("0~39", "40~79", "80~ ")) +
  theme(legend.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("0~39", "40~79", "80~ "))
```

#### 3.2.5 __IMDB count__ overview
```{r include=F}
summary(movie$imdbC)
```

```{r}
ggplot(movie, aes(x=imdbC)) +
  geom_histogram(binwidth =50000, color = 'darkblue', fill = 'lightblue') +
  labs(title = "Histogram of IMDB Count", x="IMDB Count", y="Frequency") +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))+
  scale_x_continuous(labels = label_number(scale_cut = cut_short_scale()))
```


#### 3.2.6 __Rotten Tomatoes count__ overview

```{r include=F}
summary(movie$rottentmtC)
```

```{r}
ggplot(movie, aes(x=rottentmtC)) +
  geom_histogram(binwidth =5, color = 'darkblue', fill = 'lightblue') +
  labs(title = "Histogram of Rotten Tomatoes Count", x="Rotten Tomatoes Count", y="Frequency") +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))
```

# 4. Variables EDA: Finding out Correlation


### 4.1 SMART Question: Does __rating__ affect box office performance?

```{r include=F}
# Removing outliers
nooutlierimdbR <- outlierKD2(movie, imdbR, rm=T, boxplt = T, histogram = T)
nooutlierR <- outlierKD2(nooutlierimdbR, rottentmtR, rm=T, boxplt = T, histogram = T)

summary(movie$imdbR)
summary(nooutlierR$imdbR)

summary(movie$rottentmtR)
summary(nooutlierR$rottentmtR)
```

#### 4.1.1 __IMDB Rating__ 



##### 4.1.1.1 Scatterplot and Correlation Test
```{r echo=FALSE, warning=FALSE, message=F}
# Scatterplot for imdbRating
ggplot(nooutlierR, aes(x=imdbR, y=LifetimeGross))+
  geom_point()+
  geom_smooth(method=lm) +
  labs(title = "Scatterplot of IMDB Rating", x="IMDB Rating", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5, face='bold', size=15))+
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))

# Correaltion between imdbR and earning
cor.test(nooutlierR$imdbR, nooutlierR$LifetimeGross)
```
##### 4.1.1.2 Hypothesis Test 

```{r include=F}
lowimdbR <- subset(nooutlierR, imdbR < 4)
midimdbR <- subset(nooutlierR, imdbR >= 4 & imdbR < 8)
highimdbR <- subset(nooutlierR, imdbR >= 8)
```

```{r}
ttestimdbR = t.test(midimdbR$imdbR, highimdbR$imdbR)
ttestimdbR
```

#### 4.1.2 __Rotten Tomatoes Rating__ 

##### 4.1.2.1 Scatterplot and Correlation Test
```{r}
# Scatterplot for rtRating
ggplot(nooutlierR, aes(x=rottentmtR, y=LifetimeGross))+
  geom_point()+
  geom_smooth(method=lm) +
  labs(title = "Scatterplot of Rotten Tomatoes Rating", x="Rotten Tomatoes Rating", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5, face='bold', size=15))+
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))

cor.test(nooutlierR$rottentmtR, nooutlierR$LifetimeGross)
```

##### 4.1.2.2 Hypothesis Test

```{r include=F}
lowrtR <- subset(nooutlierR, rottentmtR < 39)
midrtR <- subset(nooutlierR, rottentmtR >= 40 & imdbR < 80)
highrtR <- subset(nooutlierR, rottentmtR >= 80)
```

```{r}
# Low & Middle group ttest
ttestrtR_lowtomid <- t.test(lowrtR$rottentmtR, midrtR$rottentmtR)
ttestrtR_lowtomid
# Middle & High group ttest
ttestrtR_midtohigh <- t.test(midrtR$rottentmtR, highrtR$rottentmtR)
ttestrtR_midtohigh
```

### 4.2 SMART Question: Does __count__ affect box office performance?
```{r include=F}
# Removing outliers from count
nooutlierimdbC <- outlierKD2(movie, imdbC, rm=T, boxplt = T, histogram = T)
nooutlierC <- outlierKD2(nooutlierimdbC, rottentmtR, rm=T, boxplt = T, histogram = T)

summary(movie$imdbC)
summary(nooutlierC$imdbC)

summary(movie$rottentmtC)
summary(nooutlierC$rottentmtC)
```
#### 4.2.1 __IMDB Count__

##### 4.2.1.1 Scatterplot and Correlation Test


```{r}
# Scatterplot for imdbC
ggplot(nooutlierC, aes(x=imdbC, y=LifetimeGross))+
  geom_point()+
  geom_smooth(method=lm)+
  labs(title = "Scatterplot of IMDB Count", x="IMDB Count", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))

# Correaltion between imdbCount and gross
cor.test(nooutlierC$imdbC, nooutlierC$LifetimeGross)

```


#### 4.2.2 __Rotten Tomatoes Count__

##### 4.2.2.1 Scatterplot and Correlation Test

```{r}
# Scatterplot for rtCount
ggplot(nooutlierC, aes(x=rottentmtC, y=LifetimeGross))+
  geom_point()+
  geom_smooth(method=lm)+
  labs(title = "Scatter Plot for Rotten Tomatoes Count", x="Rotten Tomatoes Count", y="Lifetime Gross($)")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))

# Correlation between rottentmtC and gross
cor.test(nooutlierC$rottentmtC, nooutlierC$LifetimeGross)
```



# 5. Linear Regression Model

```{r includes=F}
movie_num <- subset (movie, select = -c(Title, contentR ))
movie_num <- na.omit(movie_num)
```



```{r corplot, echo=FALSE}
corm <- cor(movie_num)
corrplot.mixed(corm)
```

### 5.1 Model Fitting: Goals and Overview


### 5.2 Model Results Summary and Interpretations

  
```{r include=FALSE}
movie<- na.omit(movie)
```
  
```{r lm1, results='markup'}
lm1 <- lm(LifetimeGross~imdbC, data = movie)
summary(lm1)
```


  
```{r lm2, results='markup'}
lm2 <- lm(LifetimeGross~imdbC+rottentmtC, data = movie)
summary(lm2)
```



```{r lm3, results='markup'}
lm3 <- lm(LifetimeGross~imdbC+rottentmtC+Runtime, data = movie)
summary(lm3)
```



ANOVA: Models 1, 2, & 3
```{r anova, results='markup'}
anova(lm3, lm2, lm1)
```


  
```{r content rating lm, results='markup'}
lm4 <- lm(LifetimeGross~imdbC+rottentmtC+contentR, data = movie)
summary(lm4)

```


ANOVA: Models 2 & 4
```{r anova cont rating, results='markup'}
anova(lm4, lm2)
```

